Verifying Demonstrations

### 2020-03-11 paper/DB-Schnorr-nbit.tex
Renames DBSchnorr-n-bit to DB-Schnorr-nbit to sync with UWB

As mentioned in \cref{related-work}, while there exists a \iac{PPK} 
protocol~\cite{ProProx}, there is none for discrete logarithms. We will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.

\subsection{Reattempting a distance-bounding Schnorr protocol}%
\label{DBSchnorr-n-bit}

@@

The prover must know the responses for both challenges to successfully pass the \ac{DB} phase.
The reason for the two challenges but only one random nonce is that knowing the responses to both means learning \(\alpha\).
This allows us to prevent \ac{DBTF}.
Bundling the authentication into the distance-bounding phase (difference from Brands-Chaum) prevents \ac{DBDH}, and both adaptations together aim at \ac{DBMF} resistance. %reducing success of MF according to number of repetitions.
The reason we use secret sharing and not \(s_b\) directly, is to bound the \(l\) bits the verifier must learn of \(s_{1-b}\).
Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with secret sharing the verifier learns \(l\) bits of \emph{one share}.
Thus, we still have information theoretic security for \(s_{1-b}\)
although we reveal the \(l\) bits. (See \cref{l-bit-problem} for an
  in-depth treatment of what we call the \(l\)-bit problem.)

@@

Besides the security against the standard attacks on distance-bounding
protocols, we also need to ensure that our modification does not leak
any information to the adversary via the aforementioned \(l\) bits.

\subsection{The \(l\)-bit problem}
\label{l-bit-problem}

We will now systematically investigate the concern of the adversary
gaining any advantage from learning \(l\) bits from one of the two challenges.

@@

\endinput
\subsection{Formal Verification}

We formally verify the protocol security properties using the Tamarin
prover~\cite{meier2013tamarin}. Tamarin does not originally include
the possibility to reason on time and space in its model.  However,
thanks to a recent work by \textcite{TamarinDB}, the common properties
can be equivalently characterized with a causality-based definition
relying only on the order of messages.

The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices we made. 
It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

Tamarin's auto-prover validated the soundness and correctness
properties (in negligible computation time) and proved the security
properties used in~\cite{TamarinDB}. In the meantime,
\textcite{TamarinDBTF} introduced the notion of post-collusion
security which enabled them to prove \ac{DBTF}. In future work, we
will use this extension on our protocol.

>>>>

One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)) due to our choice of anonymous credentials whose desirable properties we list in \cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation. 
To realize this, we will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.

\subsection{Reattempting a distance-bounding Schnorr protocol}%
\label{DB-Schnorr-nbit}

@@

The prover must know the responses for both challenges to successfully pass the \ac{DB} phase.
The reason for the two challenges but only one random nonce is that knowing the responses to both means learning \(\alpha\).
This allows us to prevent \ac{DBTF}.
Bundling the authentication into the distance-bounding phase (difference from Brands-Chaum) prevents \ac{DBDH}, and both adaptations together aim at \ac{DBMF} resistance. %reducing success of MF according to number of repetitions.
The reason we use secret sharing and not \(s_b\) directly, is to bound the \(l\) bits the verifier must learn of \(s_{1-b}\).
Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with secret sharing the verifier learns \(l\) bits of \emph{one share}.
Thus, we still have information theoretic security for \(s_{1-b}\) although we reveal the \(l\) bits.

@@

\subsection{The \(l\)-bit problem}

@@

\subsection{Formal Verification}

We wanted to formally verify the protocol security properties. To realize this, 
we used the Tamarin prover~\cite{meier2013tamarin}. Tamarin does not include 
originally the possibility to reason on time and space in its model.
However, thanks to a recent work by \textcite{TamarinDB}, all the common 
properties mentioned in the previous subsection can be equivalently 
characterized with a causality-based definition relying only on the order of 
messages.

The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that we have made. 
It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

Tamarin's auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties.
This means that no trace violating the security properties is found, but the prover cannot conclusively validate that the desired properties are true. 
We are currently investigating the Tamarin interactive mode to validate as well the security properties.
